---
title: "Registration"
editor: 
  markdown: 
    wrap: 72
---

**Early-bird registration** has opened on Friday, 21<sup>st</sup> of March 2025 and will end on Wednesday, 21<sup>st</sup> of May 2025. Note that symposia can be booked independently, but for pre-conference conference courses, main conference registration is a prerequisite to be able to book.    

From Thursday, 22<sup>nd</sup> of May 2025, **late registration** fees apply.

<center>[**REGISTER HERE**](https://pcoconvin.eventsair.com/iscb25/regform/Site/Register)</center>
<br>
For questions regarding registration, please first consult the [frequently-asked-question (FAQ) page](faq.qmd), and only then contact [registrations@iscb2025.info](mailto:registrations@iscb2025.info).
<br><br>
The fees for the 2025 conference are as follows (see @nte-cond for details on the categories, and the [terms and conditions for registration](registration-terms.qmd)):

## Conference 

**Registration Entitlements**

* Attendance to all scientific sessions
* Conference material
* Access to the Exhibition Area
* Coffee breaks & lunches
* Welcome Reception attendance
* Access to the Conference proceedings

```{r, echo=F, results=F, message=F, warning=F}
library(dplyr)
library(tidyr)
library(kableExtra)

fees_source <- read.csv(file = file.path("data", "registration-fees.csv")) |> 
  mutate(Value = paste(Value, "EUR"))
  
conf_fees_source <- fees_source |> 
  filter(Purpose == "Conference") |> 
  select(-Purpose)

print_fees <- \(fees_source, registration) {
  fees_source |>
  filter(Type == registration) |>
  select(-Type) |> 
  kbl() |>
  kable_styling(full_width = TRUE) |> 
  collapse_rows(columns = 1:2, valign = "top", ) |> 
  pack_rows(registration, 1, nrow(fees_source), indent = FALSE, background = c("#EAEAEA")) |> 
  row_spec(c(2,4,6), extra_css = "border-bottom: 1px solid grey;", align = "left") |> 
  column_spec(1, extra_css = "border-bottom: 1px solid grey;")
}
```

```{r, echo=F}
gsub("<thead>.*</thead>", "", print_fees(conf_fees_source, "Early-bird registration"))
```
<br>
```{r, echo=F}
gsub("<thead>.*</thead>", "", print_fees(conf_fees_source, "Late registration"))
```


## Courses

```{r, echo=F}
courses_fees_source <- fees_source |> 
  filter(Purpose == "Courses") |> 
  select(-Purpose)
```

```{r, echo=F}
gsub("<thead>.*</thead>", "", print_fees(courses_fees_source, "Early-bird registration"))
```
<br>
```{r, echo=F}
gsub("<thead>.*</thead>", "", print_fees(courses_fees_source, "Late registration"))
```

## Mini-Symposia

```{r, echo=F}
symp_fees_source <- fees_source |> 
  filter(Purpose == "Mini-Symposia") |> 
  select(-Purpose)

```

```{r, echo=F}

early_symp_fees <-
  symp_fees_source |> 
  filter(Type == "Early-bird registration") |> 
  select(Category, Membership, Value) |> 
  kbl(col.names = NULL) |>
  kable_styling(full_width = TRUE) |> 
  pack_rows("Early-bird registration", 1, nrow(filter(symp_fees_source, Type == "Early-bird registration")), 
            indent = FALSE, background = "#EAEAEA")

gsub("<thead>.*</thead>", "", early_symp_fees)

```
<br>
```{r, echo=F}
late_symp_fees <-
  symp_fees_source |> 
  filter(Type == "Late registration") |> 
  select(Category, Membership, Value) |> 
  kbl(col.names = NULL) |>
  kable_styling(full_width = TRUE) |> 
  pack_rows("Late registration", 1, 2, indent = FALSE, background = "#EAEAEA") 

sub("<thead>.*</thead>", "", late_symp_fees)
```


## Social Dinner

```{r, echo=F}

dinner_fees <-
  fees_source |> 
  filter(Purpose == "Social Dinner") |> 
  select(Category, Value) |> 
  kbl(col.names = NULL) |>  
  kable_styling(full_width = TRUE)  

gsub("<thead>.*</thead>", "", dinner_fees)
```



::: {#nte-cond .callout-note}
## Fee category conditions
* Member fees are applicable only if membership status is active. Membership status will be verified and followed up by the ISCB Office. Please address the ISCB Office at [office@iscb.international](mailto:office@iscb.international) for membership queries.
* Reduced fees apply to low-income and medium-low-income countries considered, according to [the World Bank list for the fiscal year 2025](https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups)).
* For student registrations, a valid student ID / letter from supervisor needs to be provided through the online registration process. We reserve the right to allocate your registration to the appropriate category, in case relevant documentation is missing or is not valid.
* Retired or Senior (65+ y.o.) registration category applies ONLY for those registered to ISCB as “Retired/65+” for 2025. Membership status will be verified and followed up by the ISCB Office. Please address the ISCB Office at [office@iscb.international](mailto:office@iscb.international) for membership queries.
:::