---
title: "Registration"
editor: 
  markdown: 
    wrap: 72
---

<center>**We have reached full capacity! REGISTRATION IS NOW CLOSED!**</center>

<br>
For questions regarding registration, please first consult the [frequently-asked-question (FAQ) page](faq.qmd), and only then contact [registrations@iscb2025.info](mailto:registrations@iscb2025.info).
<br><br>
The fees for the 2025 conference are as follows (see @nte-cond for details on the categories, and the [terms and conditions for registration](registration-terms.qmd)):

## Conference 

**[Virtual attendance](faq.html#what-is-covered-by-virtual-attendance) entitlements**

* Access to live streams of the scientific sessions
* Access to Q&A during live streams
* Access to the Conference proceedings

**[Hybrid attendance](faq.html#what-is-covered-by-hybrid-attendance) entitlements**

* Attendance to all scientific sessions
* Access to live streams
* Conference material
* Access to the Exhibition Area
* Coffee breaks & lunches
* Access to the Conference proceedings

[Check your badge](badge-abbreviations.qmd) for additional entitlements, corresponding to the additional events selected during registration.

```{r, echo=F, results=F, message=F, warning=F}
library(dplyr)
library(tidyr)
library(kableExtra)

fees_source <- read.csv(file = file.path("data", "registration-fees.csv")) |> 
  mutate(Value = paste(Value, "EUR"))
  
conf_fees_source <- fees_source |> 
  filter(Purpose == "Conference") |> 
  select(-Purpose)

print_fees <- \(fees_source, registration) {
  fees_source |>
  filter(Type == registration) |>
  select(-Type) |> 
  kbl() |>
  kable_styling(full_width = TRUE) |> 
  collapse_rows(columns = 1:2, valign = "top", ) |> 
  pack_rows(registration, 1, nrow(fees_source), indent = FALSE, background = c("#EAEAEA")) |> 
  row_spec(c(2,4,6), extra_css = "border-bottom: 1px solid grey;", align = "left") |> 
  column_spec(1, extra_css = "border-bottom: 1px solid grey;")
}
```

```{r, echo=F, message=F, warning=F}
gsub("<thead>.*</thead>", "", print_fees(conf_fees_source, "Virtual attendance"))
```

## Mini-Symposia

```{r, echo=F, message=F, warning=F}
symp_fees_source <- fees_source |> 
  filter(Purpose == "Mini-Symposia") |> 
  select(-Purpose)

```


```{r, echo=F, message=F, warning=F}
late_symp_fees <-
  symp_fees_source |> 
  filter(Type == "Late registration") |> 
  select(Category, Membership, Value) |> 
  kbl(col.names = NULL) |>
  kable_styling(full_width = TRUE) |> 
  pack_rows("Late registration", 1, 2, indent = FALSE, background = "#EAEAEA") 

sub("<thead>.*</thead>", "", late_symp_fees)
```




::: {#nte-cond .callout-note}
## Fee category conditions
* Member fees are applicable only if membership status is active. Membership status will be verified and followed up by the ISCB Office. Please address the ISCB Office at [office@iscb.international](mailto:office@iscb.international) for membership queries.
* Reduced fees apply to low-income and medium-low-income countries considered, according to [the World Bank list for the fiscal year 2025](https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups)).
* For student registrations, a valid student ID / letter from supervisor needs to be provided through the online registration process. We reserve the right to allocate your registration to the appropriate category, in case relevant documentation is missing or is not valid.
* Retired or Senior (65+ y.o.) registration category applies ONLY for those registered to ISCB as “Retired/65+” for 2025. Membership status will be verified and followed up by the ISCB Office. Please address the ISCB Office at [office@iscb.international](mailto:office@iscb.international) for membership queries.
:::